Intervention Bandits

### 2015-03-13 causal-bandit/c-bandit.tex
fixes a couple of unclear bits in ucb regret section

Clearly, this is not quite the right criteria to decide when to switch ...
\subsubsection{Regret during UCB stage}

On completion of the observe stage we have tight bounds on all the arms except the first $\alpha$

Essentially, we want to know how large the regret is if we initialize with a certain number of counts already in place...

@@

Given our expression for the confidence bound in equation \ref{eqn:combinedBoundsEpsilon} we can write statement (3) as:
\eqn{
\max(T_{it},O_i) < \frac{2\alpha \log(t)}{\Delta_i^2} := \beta
}

@@

For all other arms with $\Delta_i > 0$
\eqn{
R_n(i) \leq  \frac{2\alpha \log(n)}{\Delta_i} + \frac{\Delta_i \alpha}{\alpha -2} 
}

>>>>

Clearly, this is not quite the right criteria to decide when to switch ...
\subsubsection{Regret on observing for h rounds before switching to UCB}

How large the regret is if we initialize with a certain number of counts already in place...

@@

Given our expression for the confidence bound in equation \ref{eqn:combinedBoundsEpsilon} we can write statement (3) as:
\eqn{
\max(T_{it},O_i) < \frac{2\alpha \log(t)}{\Delta_i^2}
}

Let:

\eqn{
\beta = \frac{2\alpha \log(n)}{\Delta_i^2} 
}

@@

For all other arms with $\Delta_i > 0$, the bound is the same as standard UCB
\eqn{
R_n(i) \leq  \frac{2\alpha \log(n)}{\Delta_i} + \frac{\Delta_i \alpha}{\alpha -2} 
}
